TODO LIST

### 2019-02-28 LMCS/sendrev/syntactic-clo.tex
pass on the 3-DNF example

Notice that some of these assignments, such as the one that assigns to $T$ all the variables occurring in $\theta$, are of linear size in the size of $\A_\theta$. However, $\varphi(T)$ also admits satisfying assignments of logarithmic size in the size of $\A_\theta$, such as $V(T) = \{a,b,c\}$. A key idea in the proof is the fact that the minimum of such small witnesses (under the lexicographic order induced by~$<$) can be identified by using a fixed formula:

@@

and then it can be removed also by using a fixed formula:

@@

& \hspace{23mm} (T(x')\wedge T(y')\wedge T(z')\to \ex{w}(T(w) \wedge w \neq x' \wedge w\neq y' \wedge w'\neq z))\big)

@@

In particular, the combination of these two formulae forces $T$ to represent a satisfying assignment for $\theta$ that is different from the set $\{a_0,b_0,c_0\}$, where $(a_0,b_0,c_0)$ is the minimum tuple under the lexicographic order induced by~$<$ on the set of tuples $(a,b,c)$ such that $(a \wedge b \wedge c)$ is a disjunct of $\theta$. In the proof we generalize and properly formalize this idea, thus using the existence of logarithmic size witnesses for the formulae in $\eqso(\logex{1})$ to prove that this class is closed under subtraction by one. We think that the existence of such witnesses is a fundamental property of this class that deserves to be further investigated.

>>>>

Notice that some of these assignments, such as the one that assigns to $T$ all the variables occurring in $\theta$, are of linear size in the size of $\A_\theta$. However, $\varphi(T)$ also admits satisfying assignments of logarithmic size in the size of $\A_\theta$, such as $V(T) = \{a,b,c\}$. A key idea in the proof is the fact that the minimum of such small witnesses (under the lexicographic order induced by~$<$) can be identified by using a fixed formula in $\logex{1}$:

@@

and then it can be removed also by using a fixed formula in $\logex{1}$:

@@

& \hspace{23mm} (T(x')\wedge T(y')\wedge T(z')\to \ex{w}(T(w) \wedge w \neq x' \wedge w\neq y' \wedge w'\neq z))\big).

@@

In particular, the combination of these two formulae forces $T$ to represent a satisfying assignment for $\theta$ that is different from the set $\{a_0,b_0,c_0\}$, where $(a_0,b_0,c_0)$ is the minimum tuple under the lexicographic order induced by~$<$ on the set of tuples $(a,b,c)$ such that $(a \wedge b \wedge c)$ is a disjunct of $\theta$. In the proof, we generalize and properly formalize this idea, thus using the existence of logarithmic size witnesses for the formulae in $\eqso(\logex{1})$ to prove that this class is closed under subtraction by one. We think that the existence of such witnesses is a fundamental property of this class that deserves to be further investigated.
